Parenting Observational Study E2 Coding

### 2020-03-16 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
switched to rate of JA per min

```{r echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
library(Hmisc)
theme_set(ggthemes::theme_few() + theme(legend.title = element_text(size=18), legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16), axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), axis.title.y = element_text(size=18)))
```

@@

```{r echo=F}
combine_datavyu_files <- function(data_dir) {
  d.long <- data.frame()
  files <- dir(data_dir)

@@

  # (assumes something happened early in the vid and late in the vid..)
    vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
    if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))

    jd$phase_length = jd$JointAttention.offset - jd$JointAttention.onset
    if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))
    which(jd$phase_length < 3000) # trim episodes <3 seconds long?

    id <- data.frame(SID = str_replace(f, ".csv", ""), # "012017_01_recode"
                   line = jd$JointAttention.ordinal, 
                   phase_length = jd$phase_length,
                   pja = jd$JointAttention.pJA, # was episode passive?
                   cja = jd$JointAttention.cJA,
                   bid = jd$JointAttention.bids, # parent bids (1=parent, 0=kid)
                   vid_duration = vid_duration
                )

@@

d.long[which(d.long$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)

# summarise per subject
d.raw <- d.long %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
         phase_length = phase_length / 60000) %>%
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration
```

@@

Import reliability coder's data (20 participants were coded for reliability).
```{r}
d.long_rel <- combine_datavyu_files("rel_data/")

@@

# summarise per subject
d.raw_rel <- d.long_rel %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60000, # seconds to minutes
         phase_length = phase_length / 60000) %>%
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw_rel[,2:9] = d.raw_rel[,2:9] / d.raw_rel$vid_duration

```

@@

bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")]) # .85

pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # .75 eps pass JA

cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # .75 eps coord JA

l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # .73 pass JA length

l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # .75 coord JA length
```

Inter-rater reliability is very high for number of bids, high for number of episodes of coordinated joint attention, but there is less agreement for episodes passive joint attention.

@@

ggplot(ms_bids, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Total bids for Joint Attention") +
  langcog::scale_colour_solarized() + theme(legend.position="none") 
```

@@

```{r}
ms_tja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "total_ja")

ggplot(ms_tja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total episodes of Joint Attention") +
  langcog::scale_colour_solarized() 
```

Episodes of passive joint attention.
```{r}
ms_pja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "pja")

ggplot(ms_pja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive Joint Attention")  +
  langcog::scale_colour_solarized()
```

Episodes of coordinated joint attention
```{r}
ms_cja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "cja")

ggplot(ms_cja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated Joint Attention")  +
  langcog::scale_colour_solarized()
```

Total duration of passive joint attention.
```{r}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of coordinated joint attention.
```{r}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() 
```

##Demographics

###Child gender

Total bids by gender.
```{r}
# total bids
ms_bids <- d %>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "bids")

ggplot(ms_bids, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of passive joint attention by gender
```{r}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of coordinated joint attention by gender
```{r}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() 
```

###Child age

@@

Total bids by age.
```{r}
# total bids
d$age_group = ifelse(d$age<1, "6-12", ifelse(d$age<1.5, "12-18", "18-24"))
d$age_group <- factor(d$age_group , levels = c("6-12","12-18", "18-24"))

@@

ggplot(ms_bids, aes(x = condition, y = mean, fill=age_group)) + 
  geom_bar(stat="identity", position= "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of passive joint attention by age
```{r}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, age_group) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Passive Joint Attention")  +
  langcog::scale_colour_solarized() 
```

Total duration of coordinated joint attention by age
```{r}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, age_group) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Duration Coordinated Joint Attention")  +
  langcog::scale_colour_solarized() 
```

@@

```{r}
cormat <- d %>%
  select(age, pja_length, cja_length, total_lja)
rcorr(as.matrix(cormat))
```

@@

>>>>

```{r include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
library(xtable)
library(Hmisc)
theme_set(ggthemes::theme_few() + theme(legend.title = element_text(size=18), legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16), axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), axis.title.y = element_text(size=18))) 
```

@@

```{r echo=F}
# for rate coding (JA/minute), we coded the start / end of play sessions because they were not exactly 3 minutes
play_duration <- read.csv("parenting_obs_play_duration_E2.csv", header=T)
play_duration <- play_duration %>% 
  mutate(play_duration = play_stop_sec - play_start_sec)
sort(play_duration$play_duration) # 1 pretty short session: 131 seconds
summary(play_duration$play_duration) # median = 184.5, mean=185.8
# use play_duration$verbalcue_start_sec instead of play_start? (when it exists)

combine_datavyu_files <- function(data_dir) {
  d.long <- data.frame()
  files <- dir(data_dir)

@@

    # (assumes something happened early in the vid and late in the vid..)
    #vid_duration = jd[nrow(jd),]$JointAttention.offset - jd[1,]$JointAttention.onset
    #if(vid_duration < 180000) print(paste(f, "final - first coded time is less than 180 s:",vid_duration))
    SID = str_replace(f, ".csv", "")
    vid_duration = play_duration[which(play_duration$sid==SID),]$play_duration

    jd$phase_length = jd$JointAttention.offset - jd$JointAttention.onset
    if(length(which(jd$phase_length < 0))!=0) print(paste(f, "episode with negative duration!"))

    id <- data.frame(SID = SID, 
                   line = jd$JointAttention.ordinal, 
                   phase_length = jd$phase_length,
                   pja = jd$JointAttention.pJA, # was episode passive?
                   cja = jd$JointAttention.cJA,
                   bid = jd$JointAttention.bids, # parent bids (1=parent, 0=kid)
                   vid_duration = vid_duration
                )

@@

d.long[which(d.long$phase_length<0),] # SID 121317_1  line 17          -68   1   0   1          181

d.long[which(d.long$phase_length<3000),c("cja","pja")] = 0 # any episodes <3s not counted (except bids)
# 337 / 1094

# summarise per subject
d.raw <- d.long %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60, # seconds to minutes
         phase_length = phase_length / 1000) %>% # ms to s
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute and seconds / min duration of JA)
vid_dur = d.raw$vid_duration
d.raw[,2:9] = d.raw[,2:9] / d.raw$vid_duration
d.raw$vid_duration = vid_dur
```

@@

Import reliability coder's data (25 participants were coded for reliability).
```{r}
d.long_rel <- combine_datavyu_files("rel_data/")

@@

# summarise per subject
d.raw_rel <- d.long_rel %>% group_by(SID) %>%
  mutate(vid_duration = vid_duration / 60, # seconds to minutes
         phase_length = phase_length / 1000) %>% # ms to s
  summarise(bids=sum(bid), pja_length=sum(pja*phase_length), cja_length=sum(cja*phase_length),
            pja=sum(pja), cja=sum(cja), vid_duration=vid_duration[1]) %>%
  mutate(total_ja = pja + cja, total_lja = pja_length + cja_length)

# normalize to rates (e.g., bids/minute)
d.raw_rel[,2:9] = d.raw_rel[,2:9] / d.raw_rel$vid_duration
```

@@

bids_rel = get_ICC2(d_rel[,c("bids","bids_rel")]) # .81 [.62,.91]

pja_rel = get_ICC2(d_rel[,c("pja","pja_rel")]) # .74 eps pass JA [.48,.88]

cja_rel = get_ICC2(d_rel[,c("cja","cja_rel")]) # .80 eps coord JA [.61,.91]

l_pja_rel = get_ICC2(d_rel[,c("l_pja","l_pja_rel")]) # .72 pass JA length [.44,.86]

l_cja_rel = get_ICC2(d_rel[,c("l_cja","l_cja_rel")]) # .88 coord JA length [.75,.94]
```

Inter-rater reliability is very high for length of coordinated JA (`r round(l_cja_rel$ICC, 2)`), high for bids (`r round(bids_rel$ICC, 2)`) and episodes of coordinated JA (`r round(cja_rel$ICC, 2)`), and not bad for episodes (`r round(pja_rel$ICC, 2)`) and duration of passive JA (`r round(l_pja_rel$ICC, 2)`).

@@

ggplot(ms_bids, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Bids for Joint Attention per Min.") +
  langcog::scale_colour_solarized() + theme(legend.position="none") 
```

@@

```{r, echo=F}
ms_tja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "total_ja")

ggplot(ms_tja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Episodes of JA per Min.") 
```

Episodes of passive joint attention.
```{r, echo=F}
ms_pja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "pja")

ggplot(ms_pja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive JA per Min.") 
```

Episodes of coordinated joint attention
```{r, echo=F}
ms_cja <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "cja")

ggplot(ms_cja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated JA per Min.") 
```

Rate of passive joint attention.
```{r, echo=F}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Passive JA per Min.") 
```

Rate of coordinated joint attention.
```{r, echo=F}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.")
```

## Demographics

### Child gender

Total bids by gender.

```{r, echo=F}
# total bids
ms_bids <- d %>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "bids")

ggplot(ms_bids, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Condition") + ylab("Bids for Joint Attention per Min.") # look up missing gender: "102518_6" "110418_3"
```

Rate of passive joint attention by gender
```{r, echo=F}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Passive JA per Min.") 
```

Rate of coordinated joint attention by gender

```{r, echo=F}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, gender) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill=gender)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.") 
```

### Child age

@@

Total bids by age.

```{r, echo=F}
# total bids
d$age_group = ifelse(d$age<1, "6-12", ifelse(d$age<1.5, "12-18", "18-24"))
d$age_group <- factor(d$age_group , levels = c("6-12","12-18", "18-24"))

@@

ggplot(ms_bids, aes(x = condition, y = mean, fill=age_group)) + 
  geom_bar(stat="identity", position= "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Bids for Joint Attention per Min.") 
```

Rate of passive joint attention by age

```{r, echo=F}
ms_lpja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, age_group) %>%
  multi_boot_standard(col = "pja_length")

ggplot(ms_lpja, aes(x = condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Passive JA per Min.") 
```

Rate of coordinated joint attention by age

```{r, echo=F}
ms_lcja <- d %>%
  filter(!is.na(condition))%>%
  group_by(condition, age_group) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = condition, y = mean, fill = age_group)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + ylab("Seconds of Coordinated JA per Min.") 
```

@@

```{r, echo=F}
cormat <- d %>%
  select(age, pja_length, cja_length, total_lja)
rcorr(as.matrix(cormat))
```

@@

As in Exp. 1, there is a significant effect of video condition on parental bids for JA: parents made more bids after watching an activity video. There was also a significant effect of video condition on the number of episodes of coordinated JA, as well as an interaction of condition and age.

There was a significant effect of age on the rate of episodes and duration of passive JA, and on the duration of coordinated JA.
